Poseidon Adventure

### 2019-05-10 TrueLengthCompTest.Rmd
rethinking sampling

```{r calcage2length-truth, warning=FALSE, message=FALSE}

@@

```{r lengthcensus-vis}

@@

@@

#cut down to single species
atf_survey_teststructnall <- survey_teststructnall[survey_teststructnall$species == "Arrowtooth_flounder",]
atf_survey_testresnall <- survey_testresnall[survey_testresnall$species == "Arrowtooth_flounder",]
atf_survey_testNall <- survey_testNall[survey_testNall$species == "Arrowtooth_flounder",]

length_censussurv <- calc_age2length(structn = survey_teststructnall,
                                 resn = survey_testresnall,
                                 nums = survey_testNall,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

And then `sample_fish` from `calc_age2length` output? But also we need to run `sample_fish` to get the cohort (age) output (or do we? see below) so the multinomial in there will make different distributions for smaller sample sizes. Since we are trying to represent biological sampling as one set of sampled fish which we length, then take a subset of ages and weights, this may not work.

Or, we can sum the length atoutput from calc_age2length over size bins and back in to agecl bins to get age classes, then subsample this for ages? We also have mulen and muweight for each size bin (or is it agecl bin?) so can we back the individual weights for the aged fish subsample out of this?

```{r calcage2length-breaks, eval=FALSE}
# now turn this into length comp with calc_age2length
# function takes resn and nums as inputs so run survey and sample functions on resn as well
# do we need to run the survey if calc_age2length does matching based on sample_fish?

if(initCCA) datresn <- CCAresults$resn
if(initNEUS) datresn <- NEUSresults$resn
if(initNOBA) datresn <- NOBAresults$resn

survey_testresnall <- create_survey(dat = datresn,
                                 time = timeall, # use timeall? yes to match Nall
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

#also needs structn, apply survey to this as well
if(initCCA) datstructn <- CCAresults$structn
if(initNEUS) datstructn <- NEUSresults$structn
if(initNOBA) datstructn <- NOBAresults$structn

survey_teststructnall <- create_survey(dat = datstructn,
                                 time = timeall, # use timeall? yes to match Nall
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

lengthtesthighN <- sample_fish(survey_testNall, effNhigh)
# use fish sampled from N along with survey of resn and structn in function
# calc_age2length uses nums (lengthtest) and finds matches in resn and structn

# BUT: expecting raw nums from truth, not sample_fish nums with polygon already aggregated, so this never matches as written.

# solutions, run sample_fish on structn and resn prior to input--*trying*
# or don't sameple_fish on nums first, but I think we want to sample_fish first in the workflow, then convert that sample to lengths, ages, and weights.

# unfortunately, if we are really sampling with low effN, these will be sampling cohorts with different probabilities across nums, structn, and resn, so do we need a length comp on the whole thing first and then sample it??

lengthtesthighstructn <- sample_fish(survey_teststructnall, effNhigh)
lengthtesthighresn <- sample_fish(survey_testresnall, effNhigh)

# provides ouput for an individual species and time slice
# breaks for whole dataset (NA output all rows)

length_census <- calc_age2length(structn = survey_teststructnall,
                                 resn = survey_testresnall,
                                 nums = lengthtesthigh,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

>>>>

```{r calcage2length-truth, warning=FALSE, message=FALSE, eval=FALSE}

@@

```{r lengthcensus-vis, eval=FALSE}

@@

This works, but I can't show you because I ran it line by line from the function.

@@

#cut down to single species?
atf_survey_teststructnall <- survey_teststructnall[survey_teststructnall$species == "Arrowtooth_flounder",]
atf_survey_testresnall <- survey_testresnall[survey_testresnall$species == "Arrowtooth_flounder",]
atf_survey_testNall <- survey_testNall[survey_testNall$species == "Arrowtooth_flounder",]

# still a lot
# if we apply the highest effN to structn and resn using sample fish, we should have the right atoutput for each agecl to apply to possibly subsampled nums.
# as above, apply sample_fish to resnall and structnall
# comptesthigh <- sample_fish(survey_testNall, effNhigh), but I renamed atoutput so do over without that

numsallhigh <- sample_fish(survey_testNall, effNhigh)

#dont sample these, just aggregate them
structnall <- sample_fish(survey_teststructnall, effNhigh, sample = FALSE)

resnall <-  sample_fish(survey_testresnall, effNhigh, sample = FALSE)

# now cut these down to a single species for testing
# this should still represent a census but with polygon and layer aggregated

atf_numsallhigh <- numsallhigh[numsallhigh$species == "Arrowtooth_flounder",]
atf_structnall <- structnall[structnall$species == "Arrowtooth_flounder",]
atf_resnall <- resnall[resnall$species == "Arrowtooth_flounder",]

atf_length_censussurvsamp <- calc_age2length(structn = atf_structnall,
                                 resn = atf_resnall,
                                 nums = atf_numsallhigh,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

Trying to plot just this sample, ran very quickly. And this didn't work, aggregating structural and residual N is definitely wrong.

```{r atflengthsamp1-test}

lfplot <- ggplot(atf_length_censussurvsamp$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte()

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
# lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
# lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
# lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
# lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
# lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

@@

## Back to the drawing board!

Need a couple more functions to do this correctly, see how I am [rethinking](https://sgaichas.github.io/poseidon-dev/RethinkSamplingFunctions.html).

### 2019-05-10 docs/index.Rmd
rethinking sampling

@@

>>>>

### Read this first on overall workflow

<a href="https://sgaichas.github.io/poseidon-dev/RethinkSamplingFunctions.html" target="_blank">Big picture and new functions needed - May 10, 2019</a>

@@

### Length compositions

Difficult when you don't have a good idea of the outputs you are using!

<a href="https://sgaichas.github.io/poseidon-dev/TrueLengthCompTest.html" target="_blank">Defeated by length compositions - May 8-9, 2019</a>
